Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-02-27 analysis/paper/paper.Rmd
Fixed filename error in code chunk Target_Species.

> MADELEINE: need to 'stage' the new script file when you do a 'commit' so that it gets incorporated into the commit. There isn't a copy of target_data.R in the repository yet... I set 'eval = FALSE' to skip the source call for now.
```{r Target_Species, eval=FALSE, echo=FALSE, warning = TRUE}
# selects only target species listed above
#
source("../scripts/target_data.R")
```

>>>>

```{r Target_Species, eval=TRUE, echo=FALSE, warning = TRUE}
# selects only target species listed above
#
source("../scripts/target_species.R")
```
